DOpElib - Deal Optimization Environment

### 2012-05-08 Examples/Documentation/introduction.tex
Removed some duplicated code from the ts-schemes and put it into ts_base.h resp. primal_ts_base.h. Moved the time stepping schemes to the folder tsschems
FiniteElementWrapper class from description removed
Update of the documentation.

\subsection{Problem description}
In order to allow our algorithms the automatic assembly of all required 
data we need to have some container which contains the complete problem 
description in a common data format. For this we have the following 
classes in \texttt{DOpEsrc/container}
\begin{itemize}
  \item \texttt{pdeproblemcontainer.h} Is used to describe  stationary PDE problems.
  \item \texttt{instatpdeproblemcontainer.h} {\bf TODO is still missing but will be used for nonstationary problems.} This will be implemented once we have nonstationary optimization problems running to avoid error duplication in the coding process.
  \item \texttt{optproblem.h} Is used to describe  OPT problems governed by 
    stationary PDEs. {\bf TODO should be renamed to optproblemcontainer.h including the class name!}
  \item \texttt{instatoptproblemcontainer.h} Is used to describe  OPT problems governed by nonstationary PDEs. The only difference to the stationary case is that we need to specify a time-stepping method.  
\end{itemize}
In order to fill these containers there are two things to be done,
first we need to actually write some data, for instance,
the semilinear form $a(\cdot)(\cdot)$, a target functional $J(\cdot)$, etc.,
which describe the problem. Then we have to select some numerical 
algorithm components like finite elements, linear solvers $\ldots$.
The latter ones should be written such that when exchanging these components
none of the problem descriptions should require changes. 
Note that it still may be necessary to write some additional descriptions, 
e.g., if you solve the PDE with a fix point iteration you don't need derivatives
but if you want to use Newton's method, derivatives are needed.

@@

\subsubsection{Time stepping schemes}
Third, at least for nonstationary PDEs we need to select a time stepping scheme
the file names of which are mostly self explanatory:
\begin{itemize}
\item \texttt{include/forward\underline{ }euler\underline{ }problem.h}
\item \texttt{include/shifted\underline{ }crank\underline{ }nicolson\underline{ }problem.h}
\item \texttt{include/backward\underline{ }euler\underline{ }problem.h}
\item \texttt{include/fractional\underline{ }step\underline{ }theta\underline{ }problem.h} Note that the use of this scheme requires a special Newton solver, which is, however, already
implemented for the convenience of the user!
\item \texttt{include/crank\underline{ }nicolson\underline{ }problem.h}
\end{itemize}

@@

\subsubsection{Auto-generated Problem Descriptions}
\begin{itemize}
  \item \texttt{problemdata/stateproblem.h} This is the problem description for the (forward/primal) PDE constraint.
    {\bf Similar descriptors will be build for the other problems (adjoint, tangent, $\ldots$) when time allows.}
  \item \texttt{problemdata/initialproblem.h} This is the problem descriptor to compute the finite element representation
    of the initial values. This is generated by the different time-stepping schemes based upon the defined 
    representation by the pde, which is set to the component wise $L^2$ projection by default.
  \item \texttt{problemdata/primaldirichletdata.h} This class contains the Dirichlet data for the 
    forward/primal PDE.
  \item \texttt{problemdata/tangentdirichletdata.h} This class contains the Dirichlet data for the tangent PDE, i.e.,
    the first derivative of the Dirichlet data.
  \item \texttt{problemdata/transposedgradientdirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the gradient of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
  \item \texttt{problemdata/transposedhessiandirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the hessian of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
\end{itemize}
\subsubsection{Management of Time Dependent Problems}
\begin{itemize}
\item \texttt{include/timedofhandler.h} DoFHandler responsible for the management of the timedofs (this is a part of the \texttt{SpaceTimeDoFHandler}-classes). Basically a wrapper for a $1d$ \texttt{deal.II}-DoFHandler.
\item \texttt{include/timeiterator.h} This class works as an iterator on the \texttt{TimeDoFHandler}.                 
\end{itemize}
\subsection{Wrapper classes}
\begin{itemize}
  \item \texttt{wrapper/dofhandler\underline{ }wrapper.h} A wrapper class for the \texttt{deal.II} DoFHandlers. This 
    class is needed to provide support for the \texttt{dim $= 0$} case and to have a uniform interface to 
    DoFHandler and HPDoFHandler.
  \item \texttt{wrapper/preconditioner\underline{ }wrapper.h} Contains wrappers for several of the preconditioners
    in \texttt{deal.II}. This is required since unfortunately the preconditioners in \texttt{deal.II} have different
    interfaces for their initialization.
  \item \texttt{wrapper/function\underline{ }wrapper.h} An interface that allows to use functions that depend 
    not only on space but also on time.
  \item \texttt{wrapper/snopt\underline{ }wrapper.h} An interface to the SNOPT fortran library. This is an additional
    wrapper to the one provided by SNOPT to allow automatic construction of the functions required 
    by SNOPT using our library.
  \item \texttt{wrapper/finiteelement\underline{ }wrapper.h} {\bf Will be removed soon!}
  \item \texttt{wrapper/fevalues\underline{ }wrapper.h} {\bf Will be removed soon!}
\end{itemize}

\subsection{Other}
\begin{itemize}
  \item \texttt{basic/dopetypes.h} This file contains type definitions used in the library. 
\end{itemize}

{\bf TODO! The following files need some appropriate description here 
This should be done by someone who knows what they are used for. Please move the description to the right place above.}

@@

basic:
      sth\underline{ }internals.h

include:   
            helper.h

>>>>

\subsection{Problem description}
In order to allow our algorithms the automatic assembly of all required 
data we need to have some container which contains the complete problem 
description in a common data format. For this we have the following 
classes in \texttt{DOpEsrc/container}
\begin{itemize}
  \item \texttt{pdeproblemcontainer.h} Is used to describe  stationary PDE problems.
  \item \texttt{instatpdeproblemcontainer.h} {\bf TODO is still missing but will be used for nonstationary problems.} This will be implemented once we have nonstationary optimization problems running to avoid error duplication in the coding process.
  \item \texttt{optproblemcontainer.h} Is used to describe  OPT problems governed by 
    stationary PDEs. 
  \item \texttt{instatoptproblemcontainer.h} Is used to describe  OPT problems governed by nonstationary PDEs. The only difference to the stationary case is that we need to specify a time-stepping method.  
\end{itemize}
In order to fill these containers there are two things to be done,
first we need to actually write some data, for instance,
the semilinear form $a(\cdot)(\cdot)$, a target functional $J(\cdot)$, etc.,
which describe the problem. Then we have to select some numerical 
algorithm components like finite elements, linear solvers $\ldots$.
The latter ones should be written such that when exchanging these components
none of the problem descriptions should require changes. 
Note that it still may be necessary to write some additional descriptions, 
e.g., if you solve the PDE with a fix point iteration you don't need derivatives
but if you want to use Newton's method, derivatives are needed.

@@

\subsubsection{Time stepping schemes}
Third, at least for nonstationary PDEs we need to select a time stepping scheme
the file names of which are mostly self explanatory:
\begin{itemize}
\item \texttt{tsschemes/forward\underline{ }euler\underline{ }problem.h}
\item \texttt{tsschemes/shifted\underline{ }crank\underline{ }nicolson\underline{ }problem.h}
\item \texttt{tsschemes/backward\underline{ }euler\underline{ }problem.h}
\item \texttt{tsschemes/fractional\underline{ }step\underline{ }theta\underline{ }problem.h} Note that the use of this scheme requires a special Newton solver, which is, however, already
implemented for the convenience of the user!
\item \texttt{tsschemes/crank\underline{ }nicolson\underline{ }problem.h}
\end{itemize}

@@

\subsubsection{Auto-generated Problem Descriptions}
\begin{itemize}
  \item \texttt{problemdata/stateproblem.h} This is the problem description for the (forward/primal) PDE constraint.
    {\bf Similar descriptors will be build for the other problems (adjoint, tangent, $\ldots$) when time allows.}
  \item \texttt{problemdata/initialproblem.h} This is the problem descriptor to compute the finite element representation
    of the initial values. This is generated by the different time-stepping schemes based upon the defined 
    representation by the pde, which is set to the component wise $L^2$ projection by default.
  \item \texttt{problemdata/primaldirichletdata.h} This class contains the Dirichlet data for the 
    forward/primal PDE.
  \item \texttt{problemdata/tangentdirichletdata.h} This class contains the Dirichlet data for the tangent PDE, i.e.,
    the first derivative of the Dirichlet data.
  \item \texttt{problemdata/transposedgradientdirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the gradient of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
  \item \texttt{problemdata/transposedhessiandirichletdata.h} This contains the transposed Dirichlet data needed 
    to calculate the hessian of the reduced objective functional, 
    for detail see \texttt{interfaces/transposeddirichletdatainterface.h}.
\end{itemize}
\subsubsection{Management of Time Dependent Problems}
\begin{itemize}
\item \texttt{include/timedofhandler.h} DoFHandler responsible for the management of the timedofs (this is a part of the \texttt{SpaceTimeDoFHandler}-classes). Basically a wrapper for a $1d$ \texttt{deal.II}-DoFHandler.
\item \texttt{include/timeiterator.h} This class works as an iterator on the \texttt{TimeDoFHandler}.                 
\end{itemize}
\subsection{Wrapper classes}
\begin{itemize}
  \item \texttt{wrapper/dofhandler\underline{ }wrapper.h} A wrapper class for the \texttt{deal.II} DoFHandlers. This 
    class is needed to provide support for the \texttt{dim $= 0$} case and to have a uniform interface to 
    DoFHandler and HPDoFHandler.
  \item \texttt{wrapper/preconditioner\underline{ }wrapper.h} Contains wrappers for several of the preconditioners
    in \texttt{deal.II}. This is required since unfortunately the preconditioners in \texttt{deal.II} have different
    interfaces for their initialization.
  \item \texttt{wrapper/function\underline{ }wrapper.h} An interface that allows to use functions that depend 
    not only on space but also on time.
  \item \texttt{wrapper/snopt\underline{ }wrapper.h} An interface to the SNOPT fortran library. This is an additional
    wrapper to the one provided by SNOPT to allow automatic construction of the functions required 
    by SNOPT using our library.
  \item \texttt{wrapper/fevalues\underline{ }wrapper.h} {\bf Will be removed soon!}
\end{itemize}

\subsection{Other}
\begin{itemize}
  \item \texttt{basic/dopetypes.h} This file contains type definitions used in the library. 
\item \item \texttt{basic/sth\underline{ }internals.h} Wrapper for the \texttt{MapDoFsToSupportPoints} function. The implementation of this changes with the \texttt{deal.II} version in use.
\item \texttt{include/helper.h} Collection of various small helper functions.
\item \texttt{tsschemes/primal\_ts\_base.h}  This class contains the methods which all primal time stepping schemes share.
\item \texttt{tsschemes/ts\_base.h}  This class contains the methods which all time stepping schemes share.
\end{itemize}

{\bf TODO! The following files need some appropriate description here 
This should be done by someone who knows what they are used for. Please move the description to the right place above.}.

@@
